```{r}
library(tidyverse)
```

Save the path to the folder containing LD data for our test trait pair. This trait pair has more than one overlapping QTL
```{r}
tp_folder <- "data/processed/qtl_overlaps/ld_between_peak_markers/Analysis_Results-20240111/length_Chlorothalonil.length_Arsenic_trioxide"
```

Load the input data to the LD analysis 

```{r}
overlap_input_file <- "code/qtl_overlaps/ld_between_peak_markers/toxin_length_finemapping_input_with_pheno_files.tsv"
overlaps <- data.table::fread(overlap_input_file)
```

# Filter the input data to the trait pair we are interested in

```{r}
tp_name <- basename(tp_folder)

tp_overlaps <- overlaps %>%
  filter(trait_pair == tp_name)

# check the number of rows in the filtered data
nrow(tp_overlaps)
```

Now lets clean up the data to get informatuon about the overlap intervals 

```{r}
tp_overlaps_clean <- tp_overlaps  %>% 
    select(
        CHROM_A,
        leftmost,
        rightmost,
        peak_pos
    )
```
Now lets get the unique intervals and list the unique peak_pos for each interval

```{r}
tp_overlap_ints <- tp_overlaps_clean %>%
    distinct() %>%
    group_by(CHROM_A, leftmost, rightmost) %>%
    summarise(peak_pos = paste(peak_pos, collapse = ",")) %>% 
    ungroup()
```

# Load the LD data for one overlap interval

```{r}
test_overlap <- tp_overlap_ints %>%
    slice(1)
```

```{r}
overlap_ld_file_A <- glue::glue(
    "{tp_folder}/peakPOS_A/Data/{tp_name}.{test_overlap$CHROM_A}.{test_overlap$leftmost}.{test_overlap$rightmost}.LD_inbred.tsv"
)

overlap_ld_file_B <- glue::glue(
    "{tp_folder}/peakPOS_B/Data/{tp_name}.{test_overlap$CHROM_A}.{test_overlap$leftmost}.{test_overlap$rightmost}.LD_inbred.tsv"
)

# check if the files exist
file.exists(overlap_ld_file_A)
file.exists(overlap_ld_file_B)
```


real_file_name <- "length_Chlorothalonil.length_Arsenic_trioxide.II.13521931.14347284.LD_inbred.tsv"

real_file_path <- "data/processed/qtl_overlaps/ld_between_peak_markers/Analysis_Results-20240111/length_Chlorothalonil.length_Arsenic_trioxide/peakPOS_A/Data/length_Chlorothalonil.length_Arsenic_trioxide.II.13521931.14347284.LD_inbred.tsv"

Now lets load both the files for the overlap interval

```{r}
ld_data_A <- data.table::fread(overlap_ld_file_A)

ld_data_B <- data.table::fread(overlap_ld_file_B)

# combine the two data sets

interval_ld <- bind_rows(ld_data_A, ld_data_B)

head(interval_ld)
```

For the peaks in the interval, we need to find the LD values between them 

```{r}
test_peaks <- test_overlap$peak_pos %>% str_split(",") %>% unlist() %>% as.numeric()

test_peak_1 <- test_peaks[1]
test_peak_2 <- test_peaks[2]
```

Now lets get the LD values between the two peaks

```{r}
peak_ld_values <- interval_ld %>%
    filter(
        BP_A == test_peak_1,
        BP_B == test_peak_2
    )
head(peak_ld_values)
```


