This is a script to load a list of phenotype files. For each file that we load, we are going to create a trait name that matches the traitnames in the mapping data.

# 1. Load Libraruies
```{r}
library(tidyverse)
```

# 2. Load the phenotype data
```{r}
pheno_dir <- "/projects/b1059/analysis/2021_GWA_analysis/data/traitfiles"
pheno_files <- list.files(pheno_dir, pattern = "*.tsv", full.names = TRUE)
length(pheno_files)

print(pheno_files)
```

# 3. Create a function to pull out the trait name from the file name
```{r}
get_trait_name <- function(file_path){
    file_name <- basename(file_path)
    trait_name <- str_remove(file_name, ".tsv")
    #remove the date from the trait name (everything before the first underscore)
    trait_name <- str_remove(trait_name, "^[^_]*_")
    #remove the _traitfile from the trait name
    trait_name <- str_remove(trait_name, "_traitfile")
    #replace the "." in the trait name with "_"
    trait_name <- str_replace(trait_name, "\\.", "_")
    return(trait_name)
}
```

Lets test it on the second file
```{r}
print(pheno_files[2])
get_trait_name(pheno_files[2])
```

Now lets test on the scond file wich has the concentration in the name 
```{r}
print(pheno_files[3])
get_trait_name(pheno_files[3])
```

And finally lets test on our second edge case, which has a numberic name (first file)
```{r}
print(pheno_files[1])
get_trait_name(pheno_files[1])
```

Now we want to create a dataframe with two columns, the file path and the trait name
```{r}
pheno_df <- data.frame(
    file_path = pheno_files,
    trait_name = sapply(pheno_files, get_trait_name)
)

head(pheno_df)
```

Remove the row names from `pheno_df`
```{r}
rownames(pheno_df) <- NULL
```

# 4. Load the overlapping qtl interval code
```{r}
overlaps <- data.table::fread("ld_between_peak_markers/data/test_data/toxin_length_finemapping_input.tsv")
```

# 5. Pull out toxicantA and toxicantB ids from the overlaps data by removing length_<toxicant> or CV_length_<toxicant> from traitA and traitB

First lets write a function that remove the trait type, either CV_length_<trait> or length_<trait> from the trait name
```{r}
remove_trait_type <- function(trait_name){
    if(str_detect(trait_name, "CV_length_")){
        trait_name <- str_remove(trait_name, "CV_length_")
    } else if(str_detect(trait_name, "length_")){
        trait_name <- str_remove(trait_name, "length_")
    }
    return(trait_name)
}
```

```{r}
overlaps1 <- overlaps %>%
    mutate(
        toxicantA = sapply(traitA, remove_trait_type),
        toxicantB = sapply(traitB, remove_trait_type)
    )
```

# 6. Merge the phenotype data with the overlaps data

We want to join the phenotype data for both trait A and trait B to the overlaps data. 

We also want to define a trait column that is the phenotype file for the trait that corresponds to the peak column (either peakPOSA = toxicantAor peakPOSB = toxicantB)

```{r}
overlaps2 <- overlaps1 %>%
    left_join(pheno_df, by = c("toxicantA" = "trait_name")) %>%
    rename(
        traitA_file = file_path,
        #traitA = trait_name
    ) %>%
    left_join(pheno_df, by = c("toxicantB" = "trait_name")) %>%
    rename(
        traitB_file = file_path,
        #traitB = trait_name
    )
```

If the value in the `peak` column is `peakPOS_A` then the value in traitA_file should be the value in the `traitA_file` column. If the value in the `peak` column is `peakPOS_B` then the value in traitB_file should be the value in the `traitB_file` column. 

```{r}
overlaps3 <- overlaps2 %>%
    mutate(
        trait_file = ifelse(peak == "peakPOS_A", traitA_file, traitB_file)
    )
```

# 7. Write out the overlaps data with the phenotype file names
```{r}
write.table(overlaps3, "ld_between_peak_markers/data/test_data/toxin_length_finemapping_input_with_pheno_files.tsv", sep = "\t", row.names = FALSE, quote = FALSE)
```